
%________________________________________________________________________________________
% @brief    LaTeX2e Resume for Shrutarshi Basu
% @author   Shrutarshi Basu
% @url      http://basushr.net
% @date     March 2011
% @info     Based on Latex Resume Template by Chris Paciorek 
%           http://www.biostat.harvard.edu/~paciorek/


%________________________________________________________________________________________
\documentclass[margin,line]{resume}
\usepackage{palatino}
\begin{document}
\name{\Large Shrutarshi Basu}
\begin{resume}


    %______________________________________________________________________
    % Contact Information
    \section{Contact\\Information}

    Farinon Center Box No. 8983,              \hfill 484-284-0854            \\
    111 Quad Drive, Lafayette College         \hfill me@basushr.net          \\
    Easton, PA 18042                          \hfill http://basushr.net

    %______________________________________________________________________
    % Research Interests
    \section{Professional\\Interests}

    Programming languages, virtual machines, compilers and interpreters. \\
    Hardware and software systems for concurrent and distributed computation 

    %______________________________________________________________________
    % Education
    \section{Education}

    {\bf Cornell University,} accepted to PhD Program in Computer Science,
    starting Fall 2011 \\
    {\bf Lafayette College}, PA \vspace{2mm} expecting to graduate \emph{Summa Cum Laude} in 2011%
    \begin{list2}
        \item B.S. Electrical and Computer Engineering
        \item B.A. Computer Science
        \item Current GPA: 3.82
        %% \item {\bf Relevant Courses:} Digital Circuits, Computer Organization, Software Engineering,   \\
        %%                               Programming Languages, Theory of Computation, Algorithm Analysis, Operating Systems,\\
        %%                               Signal Processing, Communications, Solid State Circuit Analysis and Design
        \item Conducting thesis work for honors in Electrical and Computer Engineering
    \end{list2}
%__________________________________________________________________________
    % Honours and Awards
    \section{Honors and\\Awards} 

    {\bf J.J. Ebers Memorial Award, 2011} for ``high academic achievement and noteworthy professional
    interest in the field of electrical engineering.''\\
    {\bf CRA Undergraduate Outstanding Research Award, 2010} -- Honorable Mention \\
    {\bf James P. Schwar Prize, 2010} awarded to a computer science student on faculty nomination \\
    {\bf William G. McClean Tau Beta Pi Engineering Prize, 2009} for ``an engineering student who has excelled in academics and extracurricular activities during the first three semesters.''
    
    Member of {\bf Tau Beta Pi} (Engineering), {\bf Eta Kappa Nu} (Electrical and Computer Engineering)
    and {\bf Upsilon Pi Epsilon} (Computer Science) Honor Societies

    %______________________________________________________________________
    % Technical experience
    \section{Technical\\ Experience}
    {\bf Operating Systems:} Linux, Mac OS X, Windows XP and Vista\\
    {\bf Programming Languages:} Python, Ruby, JavaScript, C++, C, Java, Lisp\\
    {\bf Other tools:} Git, Subversion, Qt, jQuery, JUnit, \LaTeX 

    %______________________________________________________________________
    % Professional experience
    \section{Professional\\Experience} 
    {\bf EXCEL Research Scholar} \hfill   {\sl May 2008 -- May 2009, May 2010 -- Present}
    \begin{list2}
    	\item Worked as part of a team directed by Dr. Chun Wai Liew at Lafayette College
    	\item Built a declarative programming interface and modular graphics engine for creating
          artistic patterns based on user-specified rules
    \end{list2}

    {\bf Undergraduate Researcher with PROLANGS@VT } \hfill   {\sl June 2009 -- January 2010}
    \begin{list2}
    	\item Worked under Dr. Barbara Ryder at Virginia Tech and participated in Summer REU program
    	\item Researched different dynamic program representations for use in blended analysis
    	\item Modified existing program analysis tool and used it to analyze real-world Java programs
    \end{list2}

    %______________________________________________________________________
    % Extracurricular experience
    \section{Extra-\\Curricular\\Experience} 
    
    {\bf IEEE Student Chapter President} \hfill {\sl March 2009 -- Present} \\
    Organized activities for IEEE student chapter including General Body meetings and brown bags.
    Communicated with professors, administrators and industry contacts to organize activities. 

    {\bf Residence Advisor} \hfill {\sl August 2008 -- May 2010} \\
    Organized activities for college residents, focusing on substance free activities. 
    Helped students access college resources and enforced college rules and policies.

    {\bf Foreign Language Resource Center Technical Assistant} \hfill {\sl January 2008 -- Present}\\
    Evaluated new software packages for use by foreign language students.
    Designed web templates for ePortfolios for language students and conducted ePortfolio workshops.

    %______________________________________________________________________
    % Publications

    \section{Publications}
    {\bf Exploring the impact of context sensitivity on blended analysis} \\
    Marc Fisher II, Bruno Dufour, {\bf Shrutarshi Basu} and Barbara G. Ryder.\\
    In \emph{Proceedings of the 26th IEEE International Conference
      on Software Maintenance (ICSM 2010)}.
    
    {\bf Application of formal grammars to the study of complex patterns and evolving
      systems}\\
    {\bf Shrutarshi Basu}, Rhodes Baker, Khine Lin. \\
    In \emph{Proceedings of the National Conference on Undergraduate Research, 2009}.

    \section{Research Competitions}
    {\bf Metaphor: A Declarative Approach to Computational Art} \\
    {\bf Shrutarshi Basu} and Chun Wai Liew (Advisor). 
    Accepted for Student Research Competition at \emph{The 42nd ACM Technical
      Symposium on Computer Science Education (SIGCSE 2011)}.

    \section{Projects}
    {\bf Metaphor: A declarative approach to computational art}\\
    Research project to develop software for visual artists to leverage
    computational tools. Developed a declarative programming language as an
    interface to graphical libraries written in Python.

    {\bf Parley: A concurrent object-oriented programming language}\\
    Senior honors thesis project to develop a programming language for more
    efficient use of multi-core CPUs. Implements the Actor model of computation
    in the context of a Smalltalk-like object-oriented language.

    {\bf Proctor: A prototype-based Actor library for Ruby} \\
    Implementation of thread-based concurrent Actors in Ruby using a
    prototype-based programming style. Makes extensive use of Ruby's
    metaprogramming abilities. Proof-of-concept precursor to Parley.

    {\bf Litepipe: A multithreaded server library} \\
    A simple library for writing TCP servers using a thread-per-client
    model. Includes an echo server and working on a basic HTTP server. Written
    in C using the pthreads threading library.

    {\bf WimpFi: Wireless Peer-to-peer Communications Network}\\
    A wireless short-range peer-to-peer network. Allows personals computer to
    communicate via RF-transceivers implemented on FPGAs. Implements a reduced
    version of the WiFi standard (IEEE 802.11g) with collision avoidance and
    exponential backoff. Implemented using Verilog and Xilinx synthesis tools.
    

%__________________________________________________________________________
\end{resume}
\end{document}

%__________________________________________________________________________
% EOF

