
%________________________________________________________________________________________
% @brief    LaTeX2e Resume for Shrutarshi Basu
% @author   Shrutarshi Basu
% @url      http://bytebaker.com
% @date     August 2010
% @info     Based on Latex Resume Template by Chris Paciorek 
%           http://www.biostat.harvard.edu/~paciorek/


%________________________________________________________________________________________
\documentclass[margin,line]{resume}
\usepackage{palatino}
\begin{document}
\name{\Large Shrutarshi Basu}
\begin{resume}


    %____________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}%\vspace{2mm}

%    \begin{tabular}{@{} l @{\hspace{40mm}} r}
    Farinon Center Box No. 8983,              \hfill 484-284-0854            \\
    111 Quad Drive, Lafayette College         \hfill basus@lafayette.edu    \\
    Easton, PA 18042                          \hfill http://basushr.net
%    \end{tabular}


    %____________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}

    Programming languages, virtual machines, compilers and interpreters. \\
    Hardware and software systems for concurrent and distributed computation 

    %____________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    {\bf Cornell University,} accepted to PhD Program in Computer Science,
    starting Fall 2011 \\
    {\bf Lafayette College}, PA \vspace{2mm} expecting to graduate \emph{Summa Cum Laude} in 2011%
      \begin{list2}
        \item B.S. Electrical and Computer Engineering
        \item B.A. Computer Science
        \item Current GPA: 3.82
        %% \item {\bf Relevant Courses:} Digital Circuits, Computer Organization, Software Engineering,   \\
        %%                               Programming Languages, Theory of Computation, Algorithm Analysis, Operating Systems,\\
        %%                               Signal Processing, Communications, Solid State Circuit Analysis and Design
        \item Conducting thesis work for honors in Electrical and Computer Engineering
    \end{list2}
%____________________________________________________________________________________
    % Honours and Awards
    \section{\mysidestyle Honors and\\Awards} 

    {\bf J.J. Ebers Memorial Award, 2011} for ``high academic achievement and noteworthy professional
    interest in the field of electrical engineering.''\\
    {\bf CRA Undergraduate Outstanding Research Award, 2010} -- Honorable Mention \\
    {\bf James P. Schwar Prize, 2010} awarded to a computer science student on faculty nomination \\
    {\bf William G. McClean Tau Beta Pi Engineering Prize, 2009} for ``an engineering student who has excelled in academics and extracurricular activities during the first three semesters.''
    
    Member of {\bf Tau Beta Pi} (Engineering), {\bf Eta Kappa Nu} (Electrical and Computer Engineering)
    and {\bf Upsilon Pi Epsilon} (Computer Science) Honor Societies
    
    %____________________________________________________________________________________
    % Research experience
    
    \section{\mysidestyle Research\\Experience} 
    {\bf EXCEL Research Scholar} \hfill   {\sl May 2008 -- May 2009, May 2010 -- December 2010} \\
    \begin{list2}
    	\item Worked as part of a team directed by Dr. Chun Wai Liew at Lafayette College
    	\item Researched the application of formal grammars to the generation of patterns showing a high degree of self-similarity.
    \end{list2}

    {\bf Undergraduate Researcher with PROLANGS@VT } \hfill   {\sl June 2009 -- January 2010} \\
    \begin{list2}
    	\item Worked under Dr. Barbara Ryder at Virginia Tech and participated in Summer REU program
	\item Researched different dynamic program representations for use in blended analysis
	\item Performed data gathering and analysis and modification of an existing program analysis tool
    \end{list2}

    %____________________________________________________________________________________
    %% Publications
    \section{\mysidestyle Publications}
    {\bf Exploring the impact of context sensitivity on blended analysis} \\
    Marc Fisher II, Bruno Dufour, {\bf Shrutarshi Basu} and Barbara G. Ryder.\\
    In \emph{Proceedings of the 26th IEEE International Conference on Software Maintenance (ICSM 2010)}.
    
    {\bf Application of formal grammars to the study of complex patterns and evolving systems}\\
    {\bf Shrutarshi Basu}, Rhodes Baker, Khine Lin. \\
    In \emph{Proceedings of the National Conference on Undergraduate Research, 2009}.

    %____________________________________________________________________________________
    %% Research competitions

    \section{\mysidestyle Competitions}
    {\bf Metaphor: A Declarative Approach to Computational Art} \\
    {\bf Shrutarshi Basu} and Chun Wai Liew (Advisor). 
    Accepted for Student Research Competition at \emph{The 42nd ACM Technical
      Symposium on Computer Science Education (SIGCSE 2011)}.

    %____________________________________________________________________________________
    %% Research Projects
    \section{\mysidestyle Research \\Projects}
    {\bf Metaphor: A declarative approach to computational art}\\
    Research project to develop software for visual artists to leverage
    computational tools. Developed a declarative programming language as an
    interface to Python graphical libraries.

    {\bf Parley: A concurrent object-oriented programming language}\\
    Senior honors thesis project to develop a programming language for more
    efficient use of multi-core CPUs. Implements the Actor model of computation
    in the context of a Smalltalk-like object-oriented language.

    {\bf Proctor: A prototype-based Actor library for Ruby} \\
    Implementation of thread-based concurrent Actors in Ruby using a
    prototype-based programming style. Makes extensive use of Ruby's
    metaprogramming abilities. Proof-of-concept precursor to Parley.

    %____________________________________________________________________________________
    %% Engineering Projects
    \section{\mysidestyle Engineering \\Projects}
    {\bf Litepipe: A multithreaded server library} \\
    A simple library for writing TCP servers using a thread-per-client
    model. Includes an echo server and working on a basic HTTP server.

    {\bf WimpFi: Wireless Peer-to-peer Communications Network}\\
    A wireless short-range peer-to-peer network. Allows personals computer to
    communicate via RF-transceivers implemented on FPGAs. Implements a reduced
    version of the WiFi standard (IEEE 802.11g) with collision avoidance and
    exponential backoff.
    

%________________________________________________________________________________________
\end{resume}
\end{document}

%________________________________________________________________________________________
% EOF

