%!TEX TS-program = xelatex
% Uses Curriculum Vitae template by Adrien Friggeri
% https://github.com/afriggeri/cv/
%
%
% Font And minor formatting changes by Shrutarshi Basu (2012)

\documentclass[print]{cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{Shrutarshi}{Basu}
       {programming languages and programmable systems}


% In the aside, each new line forces a line break
\begin{aside}
  \section{contact}
    Apt \#1, 220 North Quarry Street
    Ithaca, NY 14850
    ~
    \href{mailto:shr@basus.me}{\hreffont shr@basus.me}
    \href{http://basus.me}{\hreffont http://basus.me}
  \section{programming}
    C, C++, Java, Python
    OCaml, Haskell
    CSS3 \& HTML5
  \section{tools}
    Linux, OS X, \LaTeX,
\end{aside}

\section{research interests}

    Programming languages, programmable systems and networks. \\
    Hardware and software systems for concurrent and distributed computation 

\section{education}

\begin{entrylist}
  \entry
    {2011 - now}
    {PhD in Computer Science}
    {Cornell University}
    {Applied Programming Languages and Programmable Networks}
  \entry
    {2007 - 2011}
    {Dual Bachelors degree, \emph{Magna Cum Laude}}
    {Lafayette College}
    {B.S. in Electrical and Computer Engineering with Honors\\
     B.A. in Computer Science with Honors}
\end{entrylist}

\section{honors and awards}

\begin{entrylist}
  \entry
    {2011}
    {J.J. Ebers Memorial Award}
    {Lafayette College, ECE Dept.}
    {Awarded for ``high academic achievement and noteworthy professional
    interest in the field of electrical engineering.''}

  \entry
    {2010}
    {Outstanding Research Award}
    {Computer Research Association}
    {{\it Honorable mention} for research in static analysis and computer generated art}

  \entry
    {2010}
    {James P. Schwar Prize}
    {Lafayette College, CS Dept.}
    {Awarded to a computer science student on faculty nomination}

  \entry
    {2009}
    {McClean Tau Beta Pi Engineering Prize}
    {Lafayette College}
    {Awarded to ``an engineering student who has excelled in academics and extracurricular activities''}

  \entry
    {2009 - 2011}
    {Honor Society Memberships}
    {}
    {
      Member of {\bf Tau Beta Pi} (Engineering),
      {\bf Eta Kappa Nu} (Electrical and Computer Engineering)
      and {\bf Upsilon Pi Epsilon} (Computer Science) Honor Societies}
\end{entrylist}


\section{experience}

\begin{entrylist}
  \entry
    {2011 - 2012}
    {Teaching Assistant}
    {Cornell University}
    {Graduate TA for courses in data structures and functional programming}
  \entry
    {05-08 2011}
    {Software Engineering Intern}
    {GrammaTech Inc}
    {Performance improvements to the CodeSonar static analysis tool}
  \entry
    {06-12 2009}
    {Computer Science Undergraduate Researcher}
    {Virginia Tech}
    {Researched dynamic program representations for use in blended analysis}
  \entry
    {2008 - 2009\\
     2010 - 2011}
    {EXCEL Research Scholar}
    {Lafayette College}
    {Researched the application of formal grammars to the generation of fractal patterns
}
  \entry
    {2009 - 2011}
    {Foreign Language Resource Center Technical Assistant}
    {Lafayette College}
    {Evaluated educational software and design web templates for foreign
      language students. }

  \entry
    {2009 - 2011}
    {IEEE Student Chapter President}
    {Lafayette College}
    {Organized activities and meetings with the help of professors,
      administrators and industry contacts }

  \entry
    {2008 - 2010}
    {Residence Advisor}
    {Lafayette College}
    {Organized activities for college residents and helped students access
      college resources.}

\end{entrylist}

\section{projects}

\begin{entrylist}
  \entry
    {2011}
    {Freon: A novel network architecture}
    {Cornell University}
    {A novel architecture for datacenter network management using end hosts to
      perform the majority of the packet processing work. A component of the
      Frenetic project.}

  \entry
    {2011}
    {Proctor: An Actor library for Ruby}
    {Lafayette College}
    {Threaded, concurrent Actors in Ruby using a prototype-based programming
      style. Makes extensive use of Ruby's metaprogramming abilities}

  \entry
    {2010}
    {WimpFi: Wireless Peer-to-peer Communications Network}
    {Lafayette College}
    {Allows personals computer to communicate via RF-transceivers implemented on
      FPGAs. Implements a reduced version of the WiFi standard (IEEE 802.11g)
      with collision avoidance and exponential backoff.}

  \entry
    {2008-2010}
    {Metaphor: A declarative approach to computational art}
    {Lafayette College}
    {Software for visual artists to leverage computational tools. A declarative
      programming language used as an interface to graphical libraries.}


\end{entrylist}

\section{publications}
\printbibsection{inproceedings}{peer-reviewed conferences and proceedings}
\printbibsection{misc}{other publications and presentations}

\end{document}
