
%________________________________________________________________________________________
% @brief    LaTeX2e Resume for Shrutarshi Basu
% @author   Shrutarshi Basu
% @url      http://basus.me
% @date     May 2012
% @info     Based on Latex Resume Template by Chris Paciorek 
%           http://www.biostat.harvard.edu/~paciorek/


%________________________________________________________________________________________
\documentclass[margin,line]{resume}
\usepackage{palatino}
\begin{document}

\name{\Large Shrutarshi Basu}

\begin{resume}


    %______________________________________________________________________
    % Contact Information
    \section{Contact\\Information}

    Apartment \#1,                          \hfill 484-284-0854          \\
    220 North Quarry Street                 \hfill shr@basus.me          \\
    Ithaca, NY 14850                        \hfill http://basus.me

    %______________________________________________________________________
    % Education
    \section{Professional Interests}
    Applied programming languages and programmable systems. Currently building
    robust network management systems using tools and principles from the
    programming language community with a focus on high-level abstractions and
    reliability.

    %______________________________________________________________________
    % Education
    \section{Education}

    {\bf Cornell University,} PhD Program in Computer Science,
    expected graduation in 2016 \\
    \\
    {\bf Lafayette College}, PA \emph{Magna Cum Laude} in 2011%
    \begin{list2}
        \item B.S. Electrical and Computer Engineering with Honors
        \item B.A. Computer Science with Honors
    \end{list2}
    %______________________________________________________________________
    % Honours and Awards
    \section{Honors and\\Awards}

    {\bf J.J. Ebers Memorial Award, 2011} for ``high academic achievement and
    noteworthy professional interest in the field of electrical engineering.''\\
    {\bf CRA Undergraduate Outstanding Research Award, 2010} -- Honorable
    Mention \\
    {\bf James P. Schwar Prize, 2010} awarded to a computer science student on
    faculty nomination \\
    {\bf William G. McClean Tau Beta Pi Engineering Prize, 2009} for ``an
    engineering student who has excelled in academics and extracurricular
    activities during the first three semesters.''

    Member of {\bf Tau Beta Pi} (Engineering), {\bf Eta Kappa Nu} (Electrical
    and Computer Engineering) and {\bf Upsilon Pi Epsilon} (Computer Science)
    Honor Societies

    %______________________________________________________________________
    % Technical experience
    \section{Technical\\ Skills}

    {\bf Programming Languages:} Python, OCaml, C, Ruby, JavaScript, C++, Java\\
    {\bf Other tools:} Git, GNU Make, Subversion, \LaTeX, Bash

    %______________________________________________________________________
    % Professional experience
    \section{Professional\\Experience}

    {\bf Graduate Research Assistant} at Cornell University \hfill
    {\it May 2012 -- Present} \\
    Working with Dr. Nate Foster to build a distributed network management
    system involving components written in OCaml, C and Python and a Linux
    kernel module. Also responsible for managing and updating a hardware testbed.

    {\bf Software Engineering Intern} at GrammaTech Inc. \hfill
    {\it May 2011 -- August 2011} \\
    Worked on performance improvements to the CodeSonar static analysis tool.
    Gained experience in learning, navigating and improving a large C/C++
    codebase

    {\bf EXCEL Research Scholar} at Lafayette College \hfill
    {\it May 2008 -- May 2009, May 2010 -- May 2011}\\
    Worked under Dr. Chun Wai Liew to build a declarative programming interface
    and modular graphics engine for creating fractal patterns

    {\bf Undergraduate Researcher} at Virginia Tech \hfill
    {\it June 2009 -- January 2010}\\
    Worked under Dr. Barbara Ryder researching program representations for
    blended analysis. Modified existing program analysis tool and used it to
    analyze real-world Java programs

    % {\bf Technical Assistant} at Lafayette College Foreign Language Center
    % \hfill
    % {\it January 2008 -- May 2011}\\
    % Evaluated new software packages for use by foreign language students.
    % Designed web templates for language students and conducted workshops.

    \section{Projects}
    {\bf Merlin: A novel network management framework} \hfill
    {\it January 2012 -- Present }\\
    An architecture for datacenter network management using a high-level
    language to specify network policy and a distributed runtime monitor to
    implement and guarantee network properties.

    % {\bf Proctor: An Actor library for Ruby} \hfill
    % {\it January -- May 2011}\\
    % Threaded, concurrent Actors in Ruby using a prototype-based programming
    % style. Makes extensive use of Ruby's metaprogramming abilities

    {\bf WimpFi: Wireless Peer-to-peer Communications Network} \hfill
    {\it August -- Decemeber 2010}\\
    Allows personals computer to communicate via RF-transceivers implemented on
    FPGAs. Implements a reduced version of the IEEE 802.11g with collision
    avoidance and exponential backoff.

    {\bf Metaphor: A declarative approach to computational art} \hfill
    {\it May 2008 -- December 2010}\\
    Software for visual artists to leverage computational tools. A declarative
    programming language as an interface to graphical libraries.


%__________________________________________________________________________
\end{resume}
\end{document}

%__________________________________________________________________________
% EOF

