
%________________________________________________________________________________________
% @brief    LaTeX2e Resume for Shrutarshi Basu
% @author   Shrutarshi Basu
% @url      http://basus.me
% @date     October 2011
% @info     Based on Latex Resume Template by Chris Paciorek 
%           http://www.biostat.harvard.edu/~paciorek/


%________________________________________________________________________________________
\documentclass[margin,line]{resume}
\usepackage{palatino}
\begin{document}
\name{\Large Shrutarshi Basu}
\begin{resume}


    %____________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}%\vspace{2mm}

%    \begin{tabular}{@{} l @{\hspace{40mm}} r}
    Apartment 1,                            \hfill 484-284-0854            \\
    220 North Quarry Street                  \hfill shr@basus.me    \\
    Ithaca, NY 14850                         \hfill http://basus.me
%    \end{tabular}


    %____________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}

    Programming languages, programmable systems and networks. \\
    Hardware and software systems for concurrent and distributed computation 

    %____________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    {\bf Cornell University,} PhD Program in Computer Science, expected
    graduation in 2015\\
    {\bf Lafayette College} \vspace{2mm} graduated \emph{Magna Cum Laude} in 2011%
    %\begin{list1}
    \begin{list2}
        \item B.S. in Electrical and Computer Engineering
        \item B.A. in Computer Science
       %% \item {\bf Relevant Courses:} Digital Circuits, Computer Organization, Software Engineering,   \\
        %%                               Programming Languages, Theory of Computation, Algorithm Analysis, Operating Systems,\\
        %%                               Signal Processing, Communications, Solid State Circuit Analysis and Design
        \item Honors in Electrical and Computer Engineering and Computer Science
    \end{list2}
    %\end{list1}
%____________________________________________________________________________________
    % Honours and Awards
    \section{\mysidestyle Honors and\\Awards} 

    {\bf J.J. Ebers Memorial Award, 2011} for ``high academic achievement and noteworthy professional
    interest in the field of electrical engineering.''\\
    {\bf CRA Undergraduate Outstanding Research Award, 2010} -- Honorable Mention \\
    {\bf James P. Schwar Prize, 2010} awarded to a computer science student on faculty nomination \\
    {\bf William G. McClean Tau Beta Pi Engineering Prize, 2009} for ``an engineering student who has excelled in academics and extracurricular activities during the first three semesters.''
    
    Member of {\bf Tau Beta Pi} (Engineering), {\bf Eta Kappa Nu} (Electrical and Computer Engineering)
    and {\bf Upsilon Pi Epsilon} (Computer Science) Honor Societies
    
    %____________________________________________________________________________________
    % Professional experience
    
    \section{\mysidestyle Professional\\Experience} 

    {\bf Teaching Assistant at Cornell University} \hfill {\sl August 2011 --
      Present} \\
    
    \begin{list2}
      \item One of two graduate TAs for a course in data structures and
        object-oriented programming
      \item Managed a team of 15 undergraduate TAs and consultants overseeing
        grading duties
    \end{list2}


    {\bf Software Engineering Intern at GrammaTech Inc.} \hfill {\sl May 2011 -- August 2011} \\
    \begin{list2}
        \item Worked on performance improvements to the CodeSonar static analysis tool
        \item Gained experience in learning, navigating and improving a large
          C/C++ codebase
    \end{list2}

    {\bf EXCEL Research Scholar} \hfill   {\sl May 2008 -- May 2009, May 2010 --
      August 2011} \\
    \begin{list2}
    	\item Worked as part of a team directed by Dr. Chun Wai Liew at Lafayette College
    	\item Researched the application of formal grammars to the generation of patterns showing a high degree of self-similarity.
    \end{list2}

    {\bf Undergraduate Researcher with PROLANGS@VT } \hfill   {\sl June 2009 -- January 2010} \\
    \begin{list2}
    	\item Worked under Dr. Barbara Ryder at Virginia Tech and participated in Summer REU program
	\item Researched different dynamic program representations for use in blended analysis
	\item Performed data gathering and analysis and modification of an existing program analysis tool
    \end{list2}
    

    \section{\mysidestyle Extra-\\Curricular\\Experience} 
    
    {\bf IEEE Student Chapter President} \hfill {\sl March 2009 -- Present} \\
    Organizing activities for IEEE student chapter including General Body meetings and brown bags,
    communicating with professors, administrators and industry contacts to organize activities. 

    {\bf Residence Advisor} \hfill {\sl August 2008 -- May 2010} \\
    Organizing activities for college residents, focusing on substance free activities. 
    Helping students access college resources and enforcing college rules and policies.

    {\bf Foreign Language Resource Center Technical Assistant} \hfill {\sl January 2008 -- Present}\\
    Evaluating new software packages for use by foreign language students.
    Imaging, installation and troubleshooting Apple iMac computers running OS X 10.4 and 10.5.
    Designing web templates for ePortfolios for language students and conducted workshops.

    \section{\mysidestyle Publications}
    {\bf Exploring the impact of context sensitivity on blended analysis} \\
    Marc Fisher II, Bruno Dufour, {\bf Shrutarshi Basu} and Barbara G. Ryder.
    Accepted for publication in \emph{Proceedings of the 26th IEEE International Conference
      on Software Maintenance (ICSM 2010)}.
    
    {\bf Application of formal grammars to the study of complex patterns and evolving systems}\\
    {\bf Shrutarshi Basu}, Rhodes Baker, Khine Lin. In \emph{Proceedings of the National Conference on
    Undergraduate Research, 2009}.

    \section{\mysidestyle Research Competitions}
    {\bf Metaphor: A Declarative Approach to Computational Art} \\
    {\bf Shrutarshi Basu} and Chun Wai Liew (Advisor). 
    Accepted for Student Research Competition at \emph{The 42nd ACM Technical
      Symposium on Computer Science Education (SIGCSE 2011)}.

    \section{\mysidestyle Projects}
    {\bf Metaphor: A declarative approach to computational art}\\
    Research project to develop software for visual artists to leverage
    computational tools. Developed a declarative programming language as an
    interface to graphical libraries written in the Python language.

    {\bf Proctor: A prototype-based Actor library for Ruby} \\
    Implementation of thread-based concurrent Actors in Ruby using a
    prototype-based programming style. Makes extensive use of Ruby's
    metaprogramming abilities. Proof-of-concept precursor to Parley.

    {\bf Litepipe: A multithreaded server library} \\
    A simple library for writing TCP servers using a thread-per-client
    model. Includes an echo server and working on a basic HTTP server.

    {\bf WimpFi: Wireless Peer-to-peer Communications Network}\\
    A wireless short-range peer-to-peer network. Allows personals computer to
    communicate via RF-transceivers implemented on FPGAs. Implements a reduced
    version of the WiFi standard (IEEE 802.11g) with collision avoidance and
    exponential backoff.
    

%________________________________________________________________________________________
\end{resume}
\end{document}

%________________________________________________________________________________________
% EOF

